Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-11-30 manuscript/acronyms.tex
fix acronyms

\DeclareAcronym{EV}{short=EV,long=Extracellular Vesicle}
\DeclareAcronym{SVM}{long=Support Vector Machine}
\DeclareAcronym{ROC}{long=Receiver Operating Characteristic}
\DeclareAcronym{KNN}{long=K Nearest Neighbors}
\DeclareAcronym{SRA}{long=Sequence Read Archive}
\DeclareAcronym{CEA}{long=carcinoembryonic antigen}
\DeclareAcronym{GSE}{long=Gene Set Enrichment}
\DeclareAcronym{OU}{long=Ornstein-Uhlenbeck}
\DeclareAcronym{OUCH}{long=\ac{OU} Comparative Hypotheses}
\DeclareAcronym{TSI}{long=Tissue Specificity Index}
\DeclareAcronym{SRA}{long=Sequence Read Archive}
\DeclareAcronym{GH}{long=Growth Hormone}
\DeclareAcronym{PSG}{long=Pregnancy-Specific Glycoprotein}
\DeclareAcronym{PAG}{long=Pregnancy-Associated Glycoprotein}
\DeclareAcronym{GO}{long=Gene Ontology}
\DeclareAcronym{FDR}{long=False Discovery Rate}
\DeclareAcronym{gsea}{short=GSEA,long=gene set enrichment analysis}
\DeclareAcronym{FPKM}{long=Fragments Per Kilobase of exon per Million reads}

>>>>

\DeclareAcronym{EV}{short=EV,long={Extracellular Vesicle}}
\DeclareAcronym{SVM}{short=SVM,long={Support Vector Machine}}
\DeclareAcronym{ROC}{short=ROC,long={Receiver Operating Characteristic}}
\DeclareAcronym{KNN}{short=KNN,long={K Nearest Neighbors}}
\DeclareAcronym{SRA}{short=SRA,long={Sequence Read Archive}}
\DeclareAcronym{CEA}{short=CEA,long={carcinoembryonic antigen}}
\DeclareAcronym{GSE}{short=GSE,long={Gene Set Enrichment}}
%\DeclareAcronym{OU}{short=OU,long=Ornstein-Uhlenbeck}
%\DeclareAcronym{OUCH}{short=OUCH,long=\ac*{OU} Comparative Hypotheses}
\DeclareAcronym{TSI}{short=TSI,long=Tissue Specificity Index}
\DeclareAcronym{GH}{short=GH,long=Growth Hormone}
\DeclareAcronym{PSG}{short=PSG,long={Pregnancy-Specific Glycoprotein}}
\DeclareAcronym{PAG}{short=PAG,long={Pregnancy-Associated Glycoprotein}}
\DeclareAcronym{GO}{short=GO,long={Gene Ontology}}
\DeclareAcronym{FDR}{short=FDR,long={False Discovery Rate}}
\DeclareAcronym{gsea}{short=GSEA,long={gene set enrichment analysis}}
\DeclareAcronym{FPKM}{short=FPKM,long={Fragments Per Kilobase of exon per Million reads}}
